animbook: An R Package for Visualize ...

### 2023-08-01 animbook-journal.Rmd
adding list of what to write

- The data will need a following structure for it to be ready to plot: time index(time variable for the gganimate), x-axis for ggplot(this does not need to be the same as time index), key(uniqu identifier), rank(y-axis, factor variable), group(optional).

@@

>>>>

- The data will need a following structure for it to be ready to plot: time index(time variable for the gganimate), x-axis for ggplot(this does not need to be the same as time index), key(unique identifier), rank(y-axis, factor variable), group(optional).

@@

- The data structure
- The steps for the user
- How does the function processes the data
